\documentclass{article}

\usepackage{fullpage}

\title {COVID-19 }
\author{Shajeda Miah}
\date{March 19,2020}




\begin{document}



\maketitle

\section{Introduction}

Have you heard what COVID-19 is if not you better be safe. Go to the supermarket quickly before everything runs out. This worldly issue is very dangerous. Now what are you doing standing around for, go get everything you need!

\section {What is COVID-19 and how it makes a big impact}

COVID-19 stands for Corona virus. As I said in the introduction, this worldly matter is very serious. People are dying because of this virus. Schools and workplaces are closed for the safety of their staff their selves and for school the teachers, the other staff members and the students plus the principals.

\section {History}

Corona virus or COVID-19 came from China. Dr.Li Wenliang from Wuhan, China discovered this dangerous virus. Oh, but don't blame him, blame the government of China. His patients had something very unusual so Dr.Li went to the government to report this. The government was quite pissed off with him so they said that he was crazy. They threw the poor doctor in jail. But, what they did was a really really big mistake. Now because of them there is now a huge outbreak.

\section{How did COVID-19 get to America}

The first case of Corona virus in the US was in Chicago, IL. As you might know but for the people who don't know sickness spreads and what usually causes people to get COVID-19 is by handshaking. So that is how most people in the US would get COVID-19. Also there are Chinese people in the US obviously, they could have went to another Chinese person's house who came back from China shook there hand then they maybe had a meeting and in meetings you usually have to shake hands. Then that is how the virus spread.


\section{Symptoms of COVID-19}

Before you know that you have Corona virus you have to wait two weeks. The symptoms of Corona virus are flu like symptoms. You will get a cough, fever, tiredness, and have trouble breathing (in really dangerous cases.) Usually the time you are in quarantine is the same time you have COVID-19. 


\section{What should you do when you do have Corona virus}
    When you do have Corona virus do NOT call the ambulance. The doctors are already having such a hard time. They don't and can't see there families because there are so many patients in the hospital with Corona virus. As they are handling with so much Corona virus that they could spread it to their families. Give the doctors a break. What you should do is stay at home. See if you get lucky or not. This is life and death we are talking about. So for self care what you could do is sleep, drink a lot of liquids, keep warm, and take a hot shower to make it easier for you throat pain. 


\section{ How do you prevent from getting Corona virus}

    There is a way from preventing your self from COVID. Follow these five things to prevent yourself from getting COVID-19.
  1HANDS- Wash them often
  2ELBOW- Cough into it
  3FACE-  Don't touch it
  4FEET-  Stay more than 3ft apart     
  5FEEL-  sick? Stay home
 The main thing you should do to prevent getting the virus for your self is WASH YOUR HANDS!!! That is the reason why people are getting the Corona virus, it is because they handshake someone and then they don't wash there hands. Listen to this, sometimes being a clean freak is good. It is because when they handshake or touch something that another person touched they wash their hands or use hand sanitizer as fast as they can. 
 
 
 \section{ This is the end}
 
    I really hope who ever the person is who is reading this is going to  listen to my advice and stay as safe as you can. Some of my experience that I can give is that my school district closed the Dunlap schools for two weeks, but we can not open our schools on March 31. So, school might be canceled for three weeks or the rest of the year. What Dunlap planned to do is E- learning. The fourth graders are using a learning resource called Freckle. This is all from my experience. I hope you stay safe.
    



\end{document}
